%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue]{classic}%{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.85]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Andrii}
\familyname{Borovyi}
%\title{Resumé title (optional)}               % optional, remove the line if not wanted
%\address{39 Bohdana Khmelnytskoho Str., Apt.~10}{79000 Lviv}    % optional, remove the line if not wanted
\mobile{0038-097-441-8117}                    % optional, remove the line if not wanted
%\phone{0038-0352-43-6038}                      % optional, remove the line if not wanted
%\fax{fax (optional)}                          % optional, remove the line if not wanted
\email{andrii.borovyi@gmail.com}                      % optional, remove the line if not wanted
\extrainfo{Skype: aborovyi}
%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[64pt]{My_Photo}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Some quote (optional)}                 % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
\renewcommand{\refname}{Main publications}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

%\section{Objective}
% \cvline{Objective:}{Position of QA engineer}

\section{Work experience}
\cventry{2019--Present}{QA engineer}{Limelight Networks LLC.}{Lviv, Ukraine}{}{}
\cvlistitem {Creating and management for testing documentation with Atlassian's Jira and Confluence;}
\cvlistitem {Performing manual and automate testing for company's core product, using pytest, and company's own testing Frameworks;}
\cvlistitem {Creating unittests from the scratch for Bash and Perl scripts, using pytest; contributed to the testing framework;}
\cvlistitem {Running regression tests and their monitoring with Jenkins and Testrail.}

\cventry{2013--2019}{QA engineer \& Technical support}{Darwin's Grove LLC.}{Lviv, Ukraine}{}{}
\cvlistitem {Promoted usage of bug trackers (Bugzilla, Assembla) that improved QA team operability;}
\cvlistitem {Performed manual testing for desktop application and manual/automation testing for web application (nUnit, Selenium);}
\cvlistitem {Provided communication between development team and customer;}
\cvlistitem {Provided technical support on customer service calls;}
\cvlistitem {Supported company's hardware/software infrastructure, incl. users management.}
\cvline{}{}
\cvline{}{\em{}Other\em{}}
\cvlistitem {Developed a Python-based web-service for Hierarchical Temporal Memory algorithm.}

\cventry{2008--2013}{Lecturer}{Department of Information Computing Systems and Control, TNEU}{Ternopil, Ukraine}{}{}
%{\begin{itemize}
\cvlistitem {Developed Java-based course on ``Cross-platform development'' in English;}
\cvlistitem {Taught courses: ``Object-oriented programming'', ``Computer Networks'' and ``Introduction to Computer Science'' in English and Ukrainian;}
\cvlistitem {Published as a co-author a book ``Computer Networks'' in Ukrainian.}
%\end{itemize}}{}% arguments 3 to 6 are optional
\cventry{2006--2008}{Training lecturer}{Department of Information Computing Systems and Control, TNEU}{Ternopil, Ukraine}{}{}
\cvlistitem {Taught course: ``Computer Networks''.}
\cventry{2006--2011}{Researcher}{Research Institute of Intelligent Computer Systems, TNEU}{Ternopil, Ukraine}{}{}
\cvlistitem {Responsible executor for national research project ``Neural Network-based Methods for Evaluating  CPUs Consumption While Instructions Execution'' in 2011;}
\cvlistitem {Responsible executor for national research project ``Methods and Tools for Evaluating Power Consumption of Embedded Microprocessors'' in 2009-2010;}
\cvlistitem {Scholarship holder from State Scholarship Foundation of Greek Republic for research activities at Aristotle University of Thessaloníki in 2009-2010;}
\cvlistitem {Responsible executor for Greek-Ukrainian bilateral project ``Instruction Parameters Analysis for Power Modelling of Embedded Microprocessors'' in 2006-2007.}
\cventry{2003--2006}{Tester}{Department of Computer Science, TSTU}{Ternopil, Ukraine}{}{}
\cvlistitem {Administration and support of Department's domain, that includes near 40 PCs (Windows NT4.0/2000);}
\cvlistitem {Support for Department's Linux server: authorization of Windows-clients via Samba.}

\section{Education}
\cventry{2006--2012}{Ph.D. in Computer Engineering}{Ternopil National Economic University, (TNEU)}{Ternopil, Ukraine}{}{}
\cventry{2005--2006}{Master}{Ternopil State Ivan Pul'uj Technical University, (TSTU)}{Ternopil, Ukraine}{}{}
\cventry{2004--2005}{Specialist}{TSTU}{Ternopil}{}{}  % arguments 3 to 6 are optional
\cventry{2000--2004}{Bachelor}{TSTU}{Ternopil}{}{}  % arguments 3 to 6 are optional

%\newpage
\subsection{Miscellaneous}
\cventry{2006--2011}{OrgCom member}{IEEE International Conference on Intelligent Data Acquisition and Advanced Computing Systems}{Dortmund, Germany, 2007; Rende, Italy, 2009; Prague, Czech Republic, 2011}{}{Conference web-page: \url{www.idaacs.net}.}% arguments 3 to 6 are optional
\cvlistitem{Preparation of \LaTeX papers (incl. formatting of the submitted ones);}\cvlistitem{Accommodation support.}

\section{Languages}
\cvlanguage{Ukrainian}{native}{}
\cvlanguage{Russian, English}{fluent}{}
\cvlanguage{Greek}{beginner}{}

\section{Computer skills}
\cvcomputer{OS}{Debian GNU/Linux, Windows}{}{}
\cvline{Programming languages}{Python, JavaScript, Java, C\# (beginner)}
\cvcomputer{Frameworks}{Flask, React, Vue.js}{}{}{}
\cvcomputer{Testing tools}{pytest, Selenium, nUnit}{}{}
\cvcomputer{Python Libraries}{requests, SQLAlchemy, Alembic}{}{}{}
\cvcomputer{Version Control Systems}{Git, SVN}{}{}

\section{Interests}
\cvline{Software development}{\small I like to study new technologies, their intersection and application.}
\cvline{Favorite editor}{\small Vim, neo-vim, PyCharm}
\cvline{Reading} {\small I like to read books from different areas, but mainly about economy, strategies, software etc.}
\cvline{Other} {\small Addicted TED and "Talk Python to me" podcast listener.}

\end{document}

%\renewcommand{\listitemsymbol}{-} % change the symbol for lists

%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem[+]{Item 3}            % optional other symbol

%\section{Extra 2}
%\cvlistdoubleitem[\Neutral]{Item 1}{Item 4}
%\cvlistdoubleitem[\Neutral]{Item 2}{Item 5}
%\cvlistdoubleitem[\Neutral]{Item 3}{}

% Publications from a BibTeX file

%\nocite{*}
%\bibliographystyle{plainyr}
%\bibliography{publications}       % 'publications' is the name of a BibTeX file



%% end of file `template_en.tex'.
